Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-09-05 papers/paper_review/response_1.txt

REVIEWER COMMENT
----------
Figure 2:
- I don't see any squares for the field sample, is this just the background of small indistinct points?
- Very hard to see Praesepe in black and white
- Praesepe isn't very useful as a reference since the figure is considering things younger than Pleiades. However, it would be useful to see a younger comparison cluster more similar in age to Cep-Her.
RESPONSE
----------
> Yes, the field sample is the gray indistinct background.
>
> We have updated the Praesepe markers to be thicker, which improves their visibility.
>
> The attached figure rotn_ic2602_ic2391_reference.png shows a concatenation from S. Douglas (private communication) of TESS-derived rotation periods from IC-2602 and IC-2391, which are both similar in age to Cep-Her/RSG-5.  These are preliminary rotation period measurements, from the same Douglas+2021 work referenced in the manuscript, which is not yet published.  The IC-2602 and IC-2391 rotation period distributions look quite similar to those from RSG-5, though their work a) extends to lower masses, b) appears to show slightly more super-Pleiades rotation periods from F5 to G0 spectral types, and c) appears to show more stars on the fast sequence, which are lacking in the RSG-5 sample.  Given the unpublished nature of this comparison sample, and the fact that our aim is not to firmly establish the intrinsic rotational distribution of stars at this age, we prefer to leave the reference to Douglas+2021 as it is and to not include these data in the manuscript.

@@

Other minor changes made to the manuscript include:

* The radius of Kepler-1643b was previously stated in the abstract to be 2.32 +/- 0.14 R_earth.  This was a typo, it is +/- 0.13 R_earth.

* We added the follow text as a note to table 2: "\added{Users who wish to minimize field star contamination should apply more restrictive weight cuts, {\it e.g.}, $\texttt{weight}>0.1$.}"

* We have modified the axis width on all figures for visual clarity.

### 2022-09-06 papers/paper_review/response_1.txt

REVIEWER COMMENT
----------
Figure 2:
- I don't see any squares for the field sample, is this just the background of small indistinct points?
- Very hard to see Praesepe in black and white
- Praesepe isn't very useful as a reference since the figure is considering things younger than Pleiades. However, it would be useful to see a younger comparison cluster more similar in age to Cep-Her.
RESPONSE
----------
> Yes, the field sample is the gray indistinct background.
>
> We have updated the Praesepe markers to be thicker, which improves their visibility.
>
> The attached figure rotn_ic2602_ic2391_reference.png shows a concatenation from S. Douglas (private communication) of TESS-derived rotation periods from IC-2602 and IC-2391, which are both similar in age to Cep-Her/RSG-5.  These are preliminary rotation period measurements, from the same Douglas+2021 work referenced in the manuscript, which is not yet published.  The IC-2602 and IC-2391 rotation period distributions look quite similar to those from RSG-5, though their work a) extends to lower masses, b) appears to show slightly more super-Pleiades rotation periods from F5 to G0 spectral types, and c) appears to show more stars on the fast sequence, which are lacking in the RSG-5 sample.  Given the unpublished nature of this comparison sample, and the fact that our aim is not to firmly establish the intrinsic rotational distribution of stars at this age, we prefer to leave the reference to Douglas+2021 as it is and to not include these data in the manuscript.

REVIEWER COMMENT
----------
Line 280, "Generally speaking, this method is expected": It is not clear that this method of interpolation should be accurate, since it relies on changes occurring linearly in time. Since the ages are quite close to one of the anchors it is probably fine in any case. Please provide a citation or more discussion.
RESPONSE
----------
> We have added the following text: 
> \added{While in reality stellar populations do not evolve linearly in the dimensions of absolute magnitude versus color, in our case the Cep-Her loci are nearly indistinguishable from IC\,2602 (e.g., Figure~3 of \citet{bouma_kep1627_2022}).  Systematic errors incurred in the age from the non-linear evolution are therefore likely much smaller than the $\approx$10\,Myr systematic uncertainty in the absolute reference age for IC\,2602 itself \citep{david_ages_2015,randich_gaiaeso_2018}.

REVIEWER COMMENT
----------
Overall, the discussion of rotation discrepancies in Sec 2.3.2 is not clear and has the feel of the authors trying overly hard to justify their argument (I do agree with the argument, however).
- It would generally be much easier to follow this section if Fig 2 contained a younger cluster for comparison, such as the two cited at the end of this section.
- After some reflection, I think the argument about the M dwarfs is that both very young M dwarfs still in the process of contracting, and moderately young M dwarfs that have just begun to spin down, can have periods of 10-12 days. I suggest simply stating this up front, and then only consider FGK stars in the subsequent discussion.
- Line 328: "no field star outliers" - but the authors have previously stated that there is one outlier.
- 13% seems like a lot of pole-on stars for random chance, and at these young ages the amplitudes should almost always be quite large. Rampalli+2021 detects a higher fraction of rotators amongst older Praesepe stars. It seems more likely that the false positive rate is similar to the other sub-associations considered.
RESPONSE
----------
> - Regarding younger clusters for comparison, please see our response regarding Figure 2, which contains the comparison against IC-2391 and IC-2602, and our reason for not including it in the manuscript.
>
> - Regarding M dwarfs, the suggestion to exclude them by cutting at say (BP-RP)0=1.84 (Mamajek's M0V main sequence boundary) would have the following effect.  In RSG-5, it would omit 13 stars currently in the 42 star sample, including the one non-detection, and the one 12.7 day rotator.  The net result would be that 28 stars in RSG-5 would have rotation period detections consistent with being younger than the Pleaides, out of 29 expected.  In CH-2, this cut would omit 10 stars currently in the 19 star sample.  The net result would be that 8 stars in CH-2 would have rotation period detections consistent with being younger than the Pleiades, out of 9 stars expected.   We would prefer to not make this cut, chiefly because of the factor of 2x reduction in the CH-2 rotation sample.  In addition, in our view the rotation periods of the early M-dwarfs are still informative, particularly in the sense that non-detections immediately imply inconsistency with the expected >1% amplitude spot-induced modulations (e.g. Figure 10 of Rebull 2020 2020AJ....159..273R).   We have clarified the wording in the relevant paragraphs of Section 2.3.2 to emphasize the main points, which concern the range of plausible false positive rates from this analysis.  They seem to be at most one in three for CH-2 candidate members, and one in fifteen for candidate RSG-5 members.
>
>
> - Regarding "nearly no field star outliers", which was the relevant phrase, the wording has been adjusted to "only one field star outlier".  Thank you for this helpful comment.
>
> - Regarding 87/13%, please see the earlier discussion regarding the sensitivity of this fraction to our blue cutoff boundary, and the adjustment to (BP-RP)0 > 0.6, which yielded a 93% detection rate.  Given the small amplitudes of rotation-induced signals in the bluer regime, this seems like the wiser approach.  Based on the color absolute magnitude diagrams, the false positive rate in the candidate RSG-5 members is quite likely lower than in the candidate δ Lyr or CH-2 members.

REVIEWER COMMENT
----------
The discussion of vsini measurements did not provide adequate details, such as macroturbulence and potential impact of the targets being very young.
RESPONSE
----------
>  FIXME FIXME TODO TODO GET THE MACROTURBULENCE ESTIMATES FOR MAIN SEQUENCE STARS...

### 2022-09-06 papers/paper/ms.tex
update response

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$D$, defined such that the group member with the smallest core
distance has $D=1$, the group member with the greatest core
distance has $D=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$}
this procedure yields $D \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $D>0.02$ as gray points, and 
4{,}763 objects with $D>0.10$ as black points.  The 
$\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$)
and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at
$(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most
of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

@@

The CAMDs show that for RSG-5, all but one of the candidate
members are on a tight pre-main-sequence locus.  \added{Quantiatively,
88/89 stars with $\bpmrpo \geq 1.5$ are consistent with being on the
pre-main-sequence.} This implies a false
positive rate of a few percent, at most.  By comparison, our control
sample (the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population, while being outliers from the bulk
cluster population.  For CH-2, our membership selection gives 27
objects in the color range displayed, and 23 of them appear to be
consistent with being on the pre-main-sequence.  This implies a false
positive rate in CH-2 of $\approx$15\%.

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018} and 112\,Myr for the
Pleiades \citep{dahm_2015}.  These assumptions and the subsequent
processing steps taken to exclude field stars and binaries were
identical to those described in \citet{bouma_kep1627_2022}.  The mean
and uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr
for RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The older isochronal age of RSG-5 is consistent
with its location relative to the $\delta$~Lyr cluster in the upper
left panel of Figure~\ref{fig:age}.
Generally speaking, this method is expected to be accurate provided
that the metallicities of IC\,2602 and the Cep-Her groups (RSG-5,
CH-2, and the $\delta$~Lyr cluster) are roughly identical.  The
spectroscopic metallicities that we find in Section~\ref{sec:stars}
suggest that this is indeed the case.

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
\replaced{41/47}{39/42} stars have rotation periods \replaced{faster
than}{at least as fast as} the Pleiades (\replaced{87}{93}\%).  This
numerator omits the two stars with periods $>$$12$\,days visible in
the lower-left panel of Figure~\ref{fig:age}.  The age interpretation
for these latter stars, particularly the $\approx$M2.5 dwarf, is not
obvious.  \citet{rebull_usco_2018} for instance have found numerous
M-dwarfs with 10-12 day rotation periods at ages of USco
($\sim$$8$\,Myr), and some \replaced{may}{do} still exist at ages of
LCC ($\sim$$16$\,Myr; \replaced{L.~Rebull
submitted}{\citealt{2022AJ....164...80R}}).  Regardless, since nearly
no field star outliers seem to be present on the RSG-5 CAMD, the fact
that we do not detect rotation periods for $\approx$\replaced{13}{7}\%
of stars should perhaps be taken as an indication for the fraction of
stars for which rotation periods might not be detectable, due to
{e.g.}, pole-on stars having lower amplitude starspot modulation.

For CH-2, 13/19 stars have rotation periods that are obviously faster
than their counterparts in the Pleiades\deleted{ (68\%)}.  4 stars, not included
in the preceding numerator, are M-dwarfs with rotation periods between
10 and 12.5 days.  As previously noted, the age interpretation for
these M-dwarfs is not obvious.  \added{If none are cluster members,
the rotation period detection fraction is 68\%; if all are members, it
is 89\%}.
\replaced{Regardless, the $\approx$15\% false
positive rate for CH-2 determined from the CAMD seems consistent with
our fraction of detected rotation periods; RSG-5 was missing rotation
periods for $\approx$15\% of its candidate members, even though all of
its stars appear photometrically consistent with being on a single
pre-main-sequence locus.}{
This sets an upper bound on the contamination fraction in our candidate
CH-2 members at about one in three.  The true value may be as low as 
one in six, based on the earlier CAMD analysis.
}

>>>>

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$D$, defined such that the group member with the smallest core
distance has $D=1$, the group member with the greatest core
distance has $D=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$}
this procedure yields $D \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $D>0.02$ as gray points, and 
4{,}763 objects with $D>0.10$ as black points.  The 
$\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$)
and $(v_{l^*}, v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at
$(l,b)=(83^\circ,6^\circ)$, $(v_{l^*}, v_b)=(5.5 ,-3.5 )\mkms$.  Most
of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

@@

The CAMDs show that for RSG-5, all but one of the candidate
members are on a tight pre-main-sequence locus.  \added{Quantitatively,
88/89 stars with $\bpmrpo \geq 1.5$ are consistent with being on the
pre-main-sequence.} This implies a false
positive rate of a few percent, at most.  In comparison, our control
sample (the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population, while being outliers from the bulk
cluster population.  For CH-2, our membership selection gives 27
objects in the color range displayed, and 23 of them appear to be
consistent with being on the pre-main-sequence.  This
\replaced{implies}{would imply} a false
positive rate in CH-2 of $\approx$15\%.

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018} and 112\,Myr for the
Pleiades \citep{dahm_2015}.  These assumptions and the subsequent
processing steps taken to exclude field stars and binaries were
identical to those described in \citet{bouma_kep1627_2022}.  The mean
and uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr
for RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The older isochronal age of RSG-5 is consistent
with its location relative to the $\delta$~Lyr cluster in the upper
left panel of Figure~\ref{fig:age}.
Generally speaking, this method is expected to be accurate provided
that the metallicities of IC\,2602 and the Cep-Her groups (RSG-5,
CH-2, and the $\delta$~Lyr cluster) are roughly identical.  The
spectroscopic metallicities that we find in Section~\ref{sec:stars}
suggest that this is indeed the case.
\added{While in reality stellar populations do not evolve linearly in
the dimensions of absolute magnitude versus color, in our case the
Cep-Her loci are nearly indistinguishable from IC\,2602 (e.g.,
Figure~3 of \citet{bouma_kep1627_2022}).  Systematic errors incurred
in the age from the non-linear evolution are therefore likely much
smaller than the $\approx$10\,Myr systematic uncertainty in the
absolute reference age for IC\,2602 itself
\citep{david_ages_2015,randich_gaiaeso_2018}.

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
\replaced{41/47}{39/42} stars have rotation periods \replaced{faster
than}{at least as fast as} the Pleiades (\replaced{87}{93}\%).  This
numerator omits the two stars with periods $>$$12$\,days visible in
the lower-left panel of Figure~\ref{fig:age}.  The age interpretation
for these latter stars, particularly the $\approx$M2.5 dwarf, is not
obvious.  \citet{rebull_usco_2018} for instance have found numerous
M-dwarfs with 10-12 day rotation periods at ages of USco
($\sim$$8$\,Myr), and some \deleted{may} still exist at ages of
LCC ($\sim$$16$\,Myr; \replaced{L.~Rebull
submitted}{\citealt{2022AJ....164...80R}}).  Regardless, since
\replaced{nearly no field star outliers seem}{only one field star
outlier seems} to be present on the RSG-5 CAMD,
the fact
that we do not detect rotation periods for $\approx$\replaced{13}{7}\%
of stars should perhaps be taken as an indication for the fraction of
stars for which rotation periods might not be detectable, due to
{e.g.}, pole-on stars having lower amplitude starspot modulation.
\added{Field star contamination is another possible contributor.}

For CH-2, 13/19 stars have rotation periods that are obviously faster
than their counterparts in the Pleiades\deleted{ (68\%)}.  4 stars, not included
in the preceding numerator, are M-dwarfs with rotation periods between
10 and 12.5 days.  As previously noted, the age interpretation for
these M-dwarfs is \replaced{not obvious}{ambiguous}.  \added{If none are cluster members,
the rotation period detection fraction is 68\%; if all are members, it
is 89\%}.
\replaced{Regardless, the $\approx$15\% false
positive rate for CH-2 determined from the CAMD seems consistent with
our fraction of detected rotation periods; RSG-5 was missing rotation
periods for $\approx$15\% of its candidate members, even though all of
its stars appear photometrically consistent with being on a single
pre-main-sequence locus.}{
This sets an upper bound on the contamination fraction in our candidate
CH-2 members at about one in three.  Combined with the roughly one in
six contaminant rate implied by the earlier CAMD analysis, this
suggests that the sample of candidate CH-2 members is more polluted by
field stars than the RSG-5 sample.
}
